---
title: "SprintData"
author: "Stephen Kaluzny"
date: "11/16/2014"
output: html_document
---
This is an analysis of family mobile phone usages under Sprint.

# The Data
The data from the monthly Sprint bill.
It covers the months of March 2012 through September 2014.

```{r}
# Get the data from Github:
URL <- "https://raw.github.com/spkal/SprintData/master/data/sprint.txt"
tmpDataFile <- tempfile("Data")
download.file(URL, destfile=tmpDataFile, method="wget")
SprintData <- read.table(tmpDataFile, sep=" ", header=TRUE, stringsAsFactors=FALSE)
SprintData$Date <- with(SprintData,
    as.Date(paste(Year, Month, "15", sep="-"), format="%Y-%b-%d"))
SprintData$User <- as.factor(SprintData$User)
```

# Usage
The family plan included 1500 Anytime minutes.
These can be used at any time to call any phone (land or cellular).
The minutes are shared among all the users on the plan.

For the plots we will use the `dplyr` and `ggplot2` packages.
```{r}
library(dplyr)
library(ggplot2)
```

## Anytime Minutes by User
```{r}
SprintData %>%
  filter(Service == "Anytime") %>%
  ggplot(aes(Date, Unit)) + geom_line(aes(color=User)) +
  facet_grid(User ~ .)
```

## Sum of Anytime Minutes
```{r}
SprintData %>%
  group_by(Date) %>%
  filter(Service == "Anytime") %>%
  group_by(Date) %>%
  summarise(SumAnytime = sum(Unit)) %>%
  ggplot(aes(Date, SumAnytime)) + geom_line() +
  ggtitle("All Anytime Minutes by Month")
```
## Data Usage
The plan includes unlimited data usage.
Data is either S3G, S3GRoaming or S4G.
We sum those up for each user.
```{r}
SprintData %>%
  group_by(Date, User) %>%
  filter(Service == "S3G" | Service == "S3GRoaming" | Service == "S4G") %>%
  summarise(SumData = sum(Unit)) %>%
  ggplot(aes(Date, SumData)) + geom_line(aes(color=User)) +
  facet_grid(User ~ .) +
  ggtitle("Data Use by Month")
```